Computer Science House Constitution

### 2017-01-05 articles.tex
Refomat lines
Last year the document was re-formatted to have sentences be on separate
lines in order to increase readability of the source and subsequent diff
files.

\asection{Responsibilities}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\asubsection{Responsibilities of the Executive Board}
\begin{enumerate}
	\item To hold a weekly meeting specific to their responsibilities and submit notes to the House.
	\item To meet, as an Executive Board, at least weekly during the standard operating session, as defined in \ref{Standard Operating Session} to discuss and report the operations of the House.
	\item To report pertinent information to House members at the following House Meeting.
	\item To maintain records of the goals defined by each previous Executive Board.
	\item To act as a Judicial Board as defined in \ref{Judicial}.
	\item To review major projects, as defined in \ref{Expectations of House Members},  presented to them by the Evaluations director.
	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}.
	\item To respect the privacy of House members confiding in the Executive Board, barring situations related to endangerment of oneself or others, sexual assault, or in the case of a Judicial Board.
	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester.
	\item To review and update the Constitution at the end of each standard operating session, as defined in \ref{Standard Operating Session}.The constitution should remain up to date with current practices.
\end{enumerate}

>>>>

\asection{Responsibilities}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\asubsection{Responsibilities of the Executive Board}
\begin{enumerate}
	\item To hold a weekly meeting specific to their responsibilities and submit notes to the House.
	\item To meet, as an Executive Board, at least weekly during the standard operating session, as defined in \ref{Standard Operating Session} to discuss and report the operations of the House.
	\item To report pertinent information to House members at the following House Meeting.
	\item To maintain records of the goals defined by each previous Executive Board.
	\item To act as a Judicial Board as defined in \ref{Judicial}.
	\item To review major projects, as defined in \ref{Expectations of House Members},  presented to them by the Evaluations director.
	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}.
	\item To respect the privacy of House members confiding in the Executive Board, barring situations related to endangerment of oneself or others, sexual assault, or in the case of a Judicial Board.
	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester.
	\item To review and update the Constitution at the end of each standard operating session, as defined in \ref{Standard Operating Session}.
		The constitution should remain up to date with current practices.
\end{enumerate}
